\prefacesection{Acknowledgements}

The PhD journey is long and arduous. 
This thesis would not have been possible without the support of my family, advisors, mentors, and collaborators.
I'd also like to thank many friends who took part in this journey with me and made the experience unique.

First, I'd like to thank my parents.
I thank my dad for encouraging me to take on ambitious problems and not be deterred.
I thank him for pushing me to study technical topics deeply.
I thank my mom for believing in my potential.

I thank Tatsu and Carlos for being great advisors.
They have been instrumental in my growth as a researcher and as a person.
I thank them for patiently supporting me build new lines of research and contributing to various pieces.
I thank them for being kind and understanding during many unusually difficult times.
I thank them for giving me some of the best research and life advice.
I learned a tremendous amount from them, and I aspire to someday pass on the mentorship to future generations of researchers.

I thank Percy Liang for being a great mentor and for inspiring me to set high standards for myself.
I thank Florian Tramèr for teaching me many things about privacy when I first started in this area.
I thank Janardhan Kulkarni and the algorithms group at Microsoft Research Redmond for hosting me as an intern, during which time I collaborated with many others on projects that form this thesis.
I thank Mark Lemley, Dan Jurafsky, Matei Zaharia, and Michael Bernstein for mentorship on many projects.

I thank Yann, Tianyi, and Rohan for being great labmates and collaborators.
The Alpaca series of work is not included in this thesis due to topic consistency reasons. 
However, needless to say, the Alpaca series was the most exciting and rewarding piece of my PhD, and the work would not have been completed with such high quality at such speed if we did not work together.

I thank all my other mentors and collaborators for the fun experiences working together. 
This includes Peter Henderson, Daniel Kang, Ishaan Gulrajani, Yin Tat Lee, Daogao Liu, Huseyin A. Inan, Xiang Yue, Hanlin Zhang, Jiyan He, Da Yu, Huishuai Zhang, Arturs Backurs, Abhradeep Guha Thakurta, and Mitchell Gordon.

I thank many others in Hashimoto group, Guestrin group, Stanford ML group, and Stanford NLP group for being good friends. 
This includes Lisa Li, Shibani Santurkar, Niladri Chatterji, Neil Band, Nicole Meister, Mert Yuksekgonul, Yu Sun, Nelson Liu, Eric Zelikman, Qian Huang, Rishi Bommasani, Xinhao Li, Karan Dalal, Rose Wang, Ian Covert, Eric Mitchell, Archit Sharma, Rafael Rafailov, Tri Dao, Aaron Lou, Alex Wang, and many others.

Finally, I'd like to thank my mentors and friends from my time at Toronto, without whom I would not be in my current position.
I thank David Duvenaud, Jimmy Ba, Murat A. Erdogdu, and Roger Grosse for their mentorship. 
I thank Geoff Hinton for his leadership and for being a great role model.
I thank Ricky Tian Qi Chen, Guodong Zhang, Jiaxin Shi, Shengyang Sun, and many others for being great friends.